Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2022-03-22 Latex/journal_v2/version3/pr.tex
add sth:

\subsection{Main Contributions}
In this paper, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
Here, we examine a single-cell downlink system involving multiple network slices that share existing radio sources.
The main contributions of
this research are summarized as follow:
\begin{itemize}
\item 
The system has a two-time scale and should be solved in two layers. On a large-time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed. Also, the assignment of PRB to the slices is obtained. On a small-time scale, the problem of power allocation, and the assignment of PRB to UE in each slice is applied.
\item 
We consider two types of services that requires specific QoS: URLLC, which requires low latency and high reliability; and eMBB, which needs high data rate.
The problem of RAN slicing for different types of services is studied in this research.

\item 
We consider an intelligent resource allocation in the O-RAN architecture for the different services. Since conventional models do not perform well here because of the heterogeneous QoS requirements of each service type and the complexity of dynamic RAN slicing. So we must switch to machine learning and dynamic methods and find the most suitable approach.  
A dynamic strategy of resource allocation is required to solve this problem to achieve the specific QoS for each type of service in the O-RAN architecture.
 In the small-time scale, the actor-critic algorithm such as DDPG is applied to the system that is based on control policy search. This method directly searches the optimal control policy
by estimating of the gradient with respect to the parameters
of the control policy. In the large-time scale, the deep Q-Network is implemented which is a value based algorithm and it can find best solution for discrete action-state.
\end{itemize}
\section{Current State of the Research}
\subsection{System Model}
Assume we have $S$ preallocated slices serving $S$ services contains eMBB, and URLLC services; We consider $S_1$ slices for the eMBB service type and $S_2$ slices for the URLLC service type. Therefore, we have $S=S_1+S_2$.
Each Service $s\in \{1,2,...,S\} $ consists of $U_{s}$ single-antenna user equipments (UEs) which require certain QoS to be able to use the requested program.
There are different application requests which fall into one of these service categories. Each application request requires specific QoS.
Assume each slice $s \in \{1,2,...,S \}$, consists of $K_{s}$, pre-allocated physical resource blocks (PRBs) obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF. 
Virtual network functions (VNFs) are functional blocks of the system. Each VNF instance is running on a virtual machine (VM) using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
Moreover, we assume the system has $R$ single-antenna O-RU that serverd UEs cooperatively. Each O-RU $r \in \{1,2,...,R \}$ is transmitting and receiving the data of all UEs using the coordinated multipoint transmission (COMP) technology. Moreover, all O-RUs, have access to all PRBs.
\subsection{The Achievable Rate}

>>>>

\section{System Model and Problem Formulation}
\subsection{System Model}
%This paper deals with the challenges of heterogeneous vehicular and cellular networks.
Assume we have $S$ preallocated slices serving $S$ services contains eMBB, and URLLC services; We consider $S_1$ slices for the eMBB service type and $S_2$ slices for the URLLC service type. Therefore, we have $S=S_1+S_2$.
Each Service $s\in \{1,2,...,S\} $ consists of $U_{s}$ single-antenna user equipments (UEs) which require certain QoS to be able to use the requested program.
There are different application requests which fall into one of these service categories. Each application request requires specific QoS.
Assume our system consists of $K$, pre-allocated physical resource blocks (PRBs). Moreover, the system  consider to have $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP. 
Virtual network functions (VNFs) are functional blocks of the system. Each VNF instance is running on a virtual machine (VM) using resources from the data centers. 
Moreover, we assume the system has $R$ single-antenna O-RU that serverd UEs cooperatively. Each O-RU $r \in \{1,2,...,R \}$ is transmitting and receiving the data of all UEs using the coordinated multipoint transmission (COMP) technology. Moreover, all O-RUs, have access to all PRBs.
\subsection{The Achievable Rate}
The eMBB services typically use more than a one-time slot. But URLLC services use part of a time slot (mini-slot) since it has short packet transmission. In addition, the URLLC must be punctured as soon as it has requested service as it requires very low latency.
